On the minimum leaf conductance

### 2017-06-27 manuscript.Rmd
notes added

@@

It is also telling that there are few reports on the plasticity of g~0~, perhaps because it is so poorly estimated. Exceptions are @duarte2016, who found a lower g0 in a heat wave treatment (although g~1~ was unaffected), and @misson2004 who report on a close negative correlation between pre-dawn leaf water potential and g~0~.

@@

>>>>

\
Notes
gmin can increase with ozone and or aerosol particles (no ref yet) - potential for interaction with air pollution. Kerstiens?

Hoad et al; strong positive relationship between g0 and RWC - is our segmented linear method hiding changes in gmin over time?

Gardingen & Grace, gcut depends on VPD (and some useful discussion on difference isolated cuticle vs. intact leaf on non-stomatal side)

rawson and clarke 1988; gs increased hours pre-dawn in wheat. Nocturnal gs > cuticular (which was 13-50% of total)

hygen midgaard 1954- no effect of VPD on gmin (eventual decline in RWC is very linear and does not differ with various VPD treatments). "Experiments on the effect of darkening indicated that the stomata may remain partly open even during prolonged dark periods"

@@

\
It is also telling that there are few reports on the plasticity of g~0~, perhaps because it is so poorly estimated. Exceptions are @duarte2016, who found a lower g0 in a heat wave treatment (although g~1~ was unaffected), and @misson2004 who report on a close negative correlation between pre-dawn leaf water potential and g~0~.

@@

Lower g~min~ result is consistent with @duarte2016, who reported lower g~0~ and g~dark~ in a heat wave treatment (Douglas-fir), which persisted for some time. This is not due to a direct effect of temperature on in cuticular conductance, which increases with temperature (Schreiber 2001). Our results showed a large  acclimation effect but no evidence for a direct T effect (over the narrow range in T compared to Schreiber).
